---
title: "Main"
author: "Ann Atwater"
date: "2023-06-02"
output: html_document
---

```{r}
remove(list = ls());

library(tidyverse)
library(ggplot2)
library(data.table)
library(ggmap)
library(purrr)
library(lubridate)
library(reshape2)
library(texreg)
library(gtsummary)
library(kableExtra)
library(reticulate)
library(readr)
library(lmtest)
library(corrplot)
library(foreach)
library(doParallel)
library(texreg)
library(scales)
library(gt)
library(ivreg)
library(estimatr)
library(sandwich)
library(stargazer)
library(stringr)

source("04.Code/Data_Input_Functions.R")
source("04.Code/Mapping_Functions.R")
source("04.Code/T100_Functions.R")
source("04.Code/DB1B_Functions.R")
source("04.Code/descriptive_functions.R")
source("04.Code/MergerSim_Summing_MS.R")
source("04.Code/Simulation_Figures.R")
source("04.Code/SummaryTables.R")
source("04.Code/db1b_graphs.R")
source("04.Code/Plane_Graphs.R")
source("04.Code/EntryEffectsAnalysis.R")
source("04.Code/Merger_Simulation_Inspection_Code.R")
source("04.Code/Merger_Simulation.R")
source("04.Code/Stance_Analysis_Functions.R")
source("04.Code/NEA_Code.R")
source("04.Code/NEA_Graphs.R")
source("04.Code/Misc_Graphs.R")
source("04.Code/Merger_Simulation_Graphs.R")
source("04.Code/Merger_Simulation_Tables.R")
source("04.Code/Instrument_Compare_Table.R")
source("04.Code/Demand_Estimation.R")
source("04.Code/Summary_Helper_Functions.R")
source("04.Code/Merger_Anticipatory_Effects.R")
source("04.Code/SummaryGraphs.R")
source("04.Code/Simulation_Robustness.R")
source("04.Code/Merger_Simulation_Bootstrap.R")
source("04.Code/Verbal_Descriptive_Functions.R")
source("04.Code/Fee_Fix_Outcome_Compare.R")
source("04.Code/Frontier_Simulations.R")

# Load In Needed Python Package
# Set HiPerGator Path
# path_to_python <- "/usr/bin/python3"
# use_python(path_to_python)
use_condaenv("/home/annatwater/.conda/envs/jetblue")

# py_install(packages = c("pyblp", "numpy", "transformers"), pip = TRUE)

# Python Path: Work PC
# use_condaenv("C:/Users/annatwater/.conda/envs/jetblue_desktop")

py <- import_builtins()
pyblp <- import("pyblp", convert = FALSE)
np <- import("numpy")
scipy <- import("scipy")
pd <- import("pandas")
transformers <- import("transformers")

# Set up Parallel Computing Backend
registerDoParallel(cores = 1)
pycores <<- 1L

# Used for Model Estimation Across Specifications - Need Constant Throughout
# Define Model
linear_formula <- '0 + prices + NonStop + MktMilesFlown + I(MktMilesFlown**2) + Origin_Firm_Service_Ratio + Extra_Miles + Extra_Miles_Sq + Tourism + C(Year_Quarter_Effect) + C(Carrier)'
linear_component_rcl <- pyblp$Formulation(linear_formula)
linear_component_logit <- pyblp$Formulation(linear_formula)

 nonlinear_component <- pyblp$Formulation("0 + prices + NonStop + MktMilesFlown")

# Instruments for Demand Estimation
rho_instrument <- c("Num_Products_In_Market")
origin_interactions <- c("Origin_Hub", "MktMiles_OriginHub", "MktMilesSq_OriginHub",
                        "NonStop_OriginHub")
destination_interactions <- c("Destination_Hub","MktMiles_DestinationHub","MktMilesSq_DestinationHub", "NonStop_DestinationHub")
    hub_interactions <- c("Hub_Endpoint", "Hub_End_MktMiles", "Hub_End_MktMiles_Sq")
    exog_interactions <- c("MktMiles_NonStop","MktMiles_Sq_NonStop","NonStop_Origin_Share","NonStop_ExtraMiles", "MktMiles_Sq_Interact", "MktMiles_Origin_Share","MktMiles_Extra", "OriginRatio_Extra")
  
  gm_instruments <- c("GasMiles", "GasMiles_Origin_Prescence", "GasMiles_NonStop")
  
  # Stable Instruments
  instruments <- c(rho_instrument, hub_interactions, exog_interactions)
```

# Handle Data
```{r eval = TRUE}
# Prep Control Files
if(!file.exists("02.Intermediate/Clean_Codebook.Rds")){
  clean_codebook()
}

load_jet_fuel()
load_jetfuel_financial_reports() 

create_msa_pop_table()


if(!file.exists("02.Intermediate/Compile_T100.Rds")){
clean_T100(); gc()
}

if(!file.exists("02.Intermediate/Fleet_Compilation.rds")){
  clean_fleet();
}

if(!file.exists("02.Intermediate/CleanedComments.rds")){
  comments_handle()
}

unify_DB1B_Ticket(target = "02.Intermediate/Compile_DB1B_Ticket.rds"); gc();


clean_price_index()
clean_income()
covid_read_in()
state_pop_handle()
```

# DB1B Cleaning Functions
```{r}
unify_DB1B(target = "02.Intermediate/Construct_DB1B/DB1B_Initial.Rds"); gc();
clarify_DB1B(input = "02.Intermediate/Construct_DB1B/DB1B_Initial.Rds",
             output = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds"); gc();
airport_service_ratios(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
                       output = "02.Intermediate/Airport_Service_Ratios.Rds")
condense_db1b(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
              output = "02.Intermediate/Construct_DB1B/DB1B_Condensed.rds")
identify_large_airports(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
              output = "03.Output/Large_Airports.csv")
add_control_variables(input = "02.Intermediate/Construct_DB1B/DB1B_Condensed.rds",
                      output = "02.Intermediate/DB1B_With_Controls.Rds"); gc();
airport_service_ratios(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
                       output = "02.Intermediate/Merger_Service_Ratios.Rds",
                       merger = TRUE)

```

# Data Visualization
```{r}
# make_passenger_maps(); gc();
passenger_map(airlines = c("JetBlue Airways", "Spirit Air Lines"),
              years = c(2022), data = readRDS("02.Intermediate/Compile_T100.Rds"), filename = "Both_2022.pdf")
# t100_graphs(); gc(); 
plane_graphs(); gc(); 
db1b_graphics(); gc()
# overlap_graphs(); gc();
firm_revenue_graphs(); gc();
carrier_shares_graph(); 
graph_ticket_offerings()
graph_direct_ridership();
```

# Descriptive Findings 
```{r}
determine_market_firm_counts()
markets_by_hhi_increase_table()
seat_removal_table()
spirit_jetblue_overlap_cities()
oil_compare_graph()
lcc_in_market_graph()
legacy_southwest_other_graph()
spirit_revenue_sources_over_time()
spirit_jetblue_ridership_graph()
spirit_jetblue_yields_over_time()
```

# Descriptive Figures to be Reported in Text
```{r}
spirit_jetblue_near_markets_share()
```


# Stance Detection Related Analyses
```{r}
graph_stance()
comment_submitted_graph()
stance_summary_statistics()
stance_sentiment_table()
```

# Merger Pre-Effects Analysis
```{r}
merger_panel_make()
```


# Demand Estimation
# Process Data
```{r}
# Post-Pandemic
merger_sim_data_generate(years_allowed = 2021:2023,
                         output_file = "02.Intermediate/Product_Data.rds")
summary_product()
summary_product_sp_jb_focus()
summary_market()
summary_market_focus_firms()
instrument_comparison_table()


# Pre-Pandemic
merger_sim_data_generate(years_allowed = 2017:2019,
                         output_file = "02.Intermediate/prepandemic.rds")
summary_product(input = "02.Intermediate/prepandemic.rds",
                output = "06.Tables/prepandemic_SummaryStatistics_Product_Revised.tex")
summary_product_sp_jb_focus(input = "02.Intermediate/prepandemic.rds",
                            output = "06.Tables/prepandemic_SummaryStatistics_Product_FocusFirms.tex")
summary_market(input = "02.Intermediate/prepandemic.rds",
               output = "06.Tables/prepandemic_SummaryStatistics_Market.tex")
summary_market_focus_firms(input = "02.Intermediate/prepandemic.rds",
                           output = "06.Tables/prepandemic_SummaryStatistics_Market.Focus.tex")
instrument_comparison_table(input_file = "02.Intermediate/prepandemic.rds",
                            output_file = "06.Tables/prepandemic_InstrumentTable.tex")

# Two Period Summary Statistics
summary_statistics_product_two_period()
summary_statistics_market_two_period()

# Compare Table for Presentation
summary_statistics_product_two_period_compare_slim()
summary_statistics_market_compare_slim()

# 2019
merger_sim_data_generate(years_allowed = 2019,
                         output_file = "02.Intermediate/2019_data.rds")
# instrument_comparison_table(input_file = "02.Intermediate/2019_data.rds",
#                             output_file = "06.Tables/2019_InstrumentTable.tex")


```

# Random Coefficient Nested Logit
```{r}
# Post-Pandemic
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        output_file = "03.Output/random_coeff_nested_logit_results.pickle",
        precision = 1e-15); 

# Pre-Pandemic
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        input_file = "02.Intermediate/prepandemic.rds",
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, 
        nested = TRUE, precision = 1e-15,
        output_file = "03.Output/prepandemic_random_coeff_nested_logit.pickle")

rcl_two_period_table()

# Export Elasticity Comparison Table
elasticity_compare_table()
```

```{r}
combined_rcl_output_table()
rcl_two_period_table_present()

sim_data <- readRDS("03.Output/Adv_Merger_Sim_Data.rds")
sim_data[, Profits.MeanCost := (Prices.MeanCost.Sim - costs.mean) * 100 * Shares.MeanCost.Sim * Potential_Passengers]
```


# Merger Simulation
```{r}
# Post-Pandemic
merger_simulation_advanced(); gc(); gc();

# Pre-Pandemic
merger_simulation_advanced(model_in = "03.Output/prepandemic_random_coeff_nested_logit.pickle",
                           data_in = "02.Intermediate/prepandemic.rds",
                           data_out = "03.Output/PrePandemic_Adv_Merger_Sim_Data.rds"); gc(); gc(); 
merger_results_table()
minimum_fare_increase_table()
merger_change_pass_graph()

change_minimum_fare()
change_minimum_fare(merger_data.basic  = "03.Output/PrePandemic_Basic_Merger_Sim_Data.rds", 
                    merger_data.adv = "03.Output/PrePandemic_Adv_Merger_Sim_Data.rds",
                    observed_data = "02.Intermediate/prepandemic.rds",
                    graph_out.internalize = "05.Figures/PrePandemic_Merger_Change_MinimumFare_Internalize.pdf",
                    graph_out.BestCase = "05.Figures/PrePandemic_Merger_Change_MinimumFare_BestCase.pdf",
                    graph_out.AverageCase = "05.Figures/PrePandemic_Merger_Change_MinimumFare_AverageCase.pdf",
                    graph_out.WorstCase = "05.Figures/PrePandemic_Merger_Change_MinimumFare_WorstCase.pdf",
                    graph_out = "05.Figures/PrePandemic_Merger_Change_MinimumFare.pdf")
merger_change_pass_graph(merger_data = "03.Output/PrePandemic_Adv_Merger_Sim_Data.rds",
                    observed_data = "02.Intermediate/prepandemic.rds",
                    graph_out.bestCase = "05.Figures/PrePandemic_Merger_Change_Passengers_BestCase.pdf",
         graph_out.averageCase = "05.Figures/PrePandemic_Merger_Change_Passengers_AverageCase.pdf",
         graph_out.worstCase = "05.Figures/PrePandemic_Merger_Change_Passengers_WorstCase.pdf")

minimum_fare_increase_table()
minimum_fare_increase_table(table_out = "06.Tables/MinimumFareChange_25Increment.tex",
                            buckets = c("$<$ 0", "0-25", "25-50", "50-75",
                                                    "75-100", "100 $<$"),
                                        break_points = c(-Inf, 0, 25, 50, 75, 100, Inf))
minimum_fare_percent_increase_table()
minimum_fare_percent_increase_table(table_out = "06.Tables/MinimumFareChange_Percent_25Increment.tex",
                                    buckets = c("$<$ 0", "0-25", "25-50", "50-75",
                                                    "75-100", "100 $<$"),
                                        break_points = c(-Inf, 0, 25, 50, 75, 100, Inf))

merger_simulation_hhi_change()
merger_simulation_cs_table()
change_average_fare_dist()
change_average_fare_dist(merger_data.adv = "03.Output/PrePandemic_Adv_Merger_Sim_Data.rds",
                                     observed_data = "02.Intermediate/prepandemic.rds",
                                     graph_out.raw = "05.Figures/PrePandemic_Merger_Change_AverageFare_Dist.pdf",
                                     graph_out.percent = "05.Figures/PrePandemic_Merger_Change_AverageFare_Dist_Percent.pdf")
change_minimum_fare_dist()
change_minimum_fare_dist(merger_data = "03.Output/PrePandemic_Adv_Merger_Sim_Data.rds",
                                     observed_data = "02.Intermediate/prepandemic.rds",
                                     graph_out = "05.Figures/PrePandemic_Merger_Change_MinimumFare_Dist.pdf",
                                     graph_out.percent = "05.Figures/PrePandemic_Merger_Change_MinimumFare_Percent_Dist.pdf")

# Simulations with Efficiencies Assumed
merger_results_table_10_efficiency()
merger_results_table_5_efficiency()

```

# Heterogeneity Explore - Graph Marginal Costs
```{r}
marginal_cost_distribution(Carrier = "Spirit Air Lines", Markets = "Contested",
                           graph_out = "05.Figures/MC_Plot_Spirit_PostPandemic.pdf")
marginal_cost_distribution(Carrier = "JetBlue Airways", Markets = "Contested",
                           graph_out = "05.Figures/MC_Plot_JB_PostPandemic.pdf")
marginal_cost_distribution(model_in = "03.Output/prepandemic_random_coeff_nested_logit.pickle",
                           data_in = "02.Intermediate/prepandemic.rds",
                           Carrier = "Spirit Air Lines", Markets = "Contested",
                           graph_out = "05.Figures/MC_Plot_Spirit_PrePandemic.pdf")
marginal_cost_distribution(model_in = "03.Output/prepandemic_random_coeff_nested_logit.pickle",
                           data_in = "02.Intermediate/prepandemic.rds",
                           Carrier = "JetBlue Airways", Markets = "Contested",
                           graph_out = "05.Figures/MC_Plot_JB_PrePandemic.pdf")

marginal_cost_difference_graph(); gc(); gc()
marginal_cost_difference_graph(model_in = "03.Output/prepandemic_random_coeff_nested_logit.pickle",
                           data_in = "02.Intermediate/prepandemic.rds",
                           graph_out = "05.Figures/Marginal_Cost_Prepandemic_Difference_Graph.pdf"); gc(); gc();
```


# Robustness Check - Scale Auxilary Fares Added In
```{r}
condense_db1b(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
              output = "02.Intermediate/Construct_DB1B/Auxilary_Scale_DB1B_Condensed.rds",
              auxilary_mode = "scale")
add_control_variables(input = "02.Intermediate/Construct_DB1B/Auxilary_Scale_DB1B_Condensed.rds",
                      output = "02.Intermediate/Auxilary_Scale_DB1B.Rds"); gc()

# # Merger Sim Generate # #
merger_sim_data_generate(years_allowed = 2021:2023,
                         input_file = "02.Intermediate/Auxilary_Scale_DB1B.Rds",
                         output_file = "02.Intermediate/Auxilary_Scale_postpandemic.rds")


# Pre-Pandemic
merger_sim_data_generate(years_allowed = 2017:2019,
                         input_file = "02.Intermediate/Auxilary_Scale_DB1B.Rds",
                         output_file = "02.Intermediate/Auxilary_Scale_prepandemic.rds")


# Instrument Tables
instrument_comparison_table(input_file = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
      output_file = "06.Tables/Auxilary_Scale_Instrument_Compare_Table.tex")
instrument_comparison_table(input_file = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
      output_file = "06.Tables/Auxilary_Scale_Prepandemic_Instrument_Compare_Table.tex")


# Estimate Models
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        input_file = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
        output_file = "03.Output/Auxilary_Scale_postpandemic_model.pickle",
        precision = 1e-15); 
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        input_file = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
        output_file = "03.Output/Auxilary_Scale_prepandemic_model.pickle",
        precision = 1e-15)

rcl_two_period_table(post_in = "03.Output/Auxilary_Scale_postpandemic_model.pickle",
                     post_data_in = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
                     pre_in = "03.Output/Auxilary_Scale_prepandemic_model.pickle",
                     pre_data_in = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
                     output_table = "06.Tables/Auxilary_Scale_RCL_Both_Period_Output.tex")

# Merger Simulation 
merger_simulation_advanced(model_in = "03.Output/Auxilary_Scale_prepandemic_model.pickle",
                           data_in = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
                           data_out = "03.Output/Auxilary_Scale_Prepandemic_Merger.rds"); gc(); gc(); 

merger_simulation_advanced(model_in = "03.Output/Auxilary_Scale_postpandemic_model.pickle",
                           data_in = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
                           data_out = "03.Output/Auxilary_Scale_Postpandemic_Merger.rds"); gc(); gc()
# Output Tables
merger_results_table(merger_post  = "03.Output/Auxilary_Scale_Postpandemic_Merger.rds",
                     observed_post = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
                     merger_pre =  "03.Output/Auxilary_Scale_Prepandemic_Merger.rds",
                     observed_pre = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
                     table_out = "06.Tables/Auxilary_Scale_Merger_Results.tex")


minimum_fare_increase_table(
  merger_data.post = "03.Output/Auxilary_Scale_Postpandemic_Merger.rds",
  observed.post = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
  merger_data.pre =  "03.Output/Auxilary_Scale_Prepandemic_Merger.rds",
  observed.pre = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
  table_out = "06.Tables/Auxilary_Scale_MinimumFareChange.tex")

minimum_fare_percent_increase_table(merger_data.post = "03.Output/Auxilary_Scale_Postpandemic_Merger.rds",
  observed.post = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
  merger_data.pre =  "03.Output/Auxilary_Scale_Prepandemic_Merger.rds",
  observed.pre = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
  table_out = "06.Tables/Auxilary_Scale_MinimumFareChange_Percent.tex")

merger_simulation_cs_table(merger_post = "03.Output/Auxilary_Scale_Postpandemic_Merger.rds",
                           observed_post = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
                           merger_pre = "03.Output/Auxilary_Scale_Prepandemic_Merger.rds",
                           observed_pre = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
                           table_out = "06.Tables/Ancillary_Scale_Merger_CS_Results.tex")

# With Assumed Efficiencies from Merger
merger_results_table_10_efficiency(merger_post = "03.Output/Auxilary_Scale_Postpandemic_Merger.rds",
                                  observed_post = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
                                  merger_pre = "03.Output/Auxilary_Scale_Prepandemic_Merger.rds",
                                  observed_pre = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
                                  table_out = "06.Tables/Auxilary_Scale_Results_10Percent_Efficient.tex")

merger_results_table_5_efficiency(merger_post = "03.Output/Auxilary_Scale_Postpandemic_Merger.rds",
                                  observed_post = "02.Intermediate/Auxilary_Scale_postpandemic.rds",
                                  merger_pre = "03.Output/Auxilary_Scale_Prepandemic_Merger.rds",
                                  observed_pre = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
                                  table_out = "06.Tables/Auxilary_Scale_Results_5Percent_Efficient.tex")

```

Additional Descriptive Graphs
```{r}
airfare_trend_graph()
```


# Compare Marginal Costs Recovered with/without Fee Fix
```{r}
# Generate Data Tables with Both MC Contained
product_mc_compare_generate();
product_mc_compare_generate(model_in_unadjust = "03.Output/prepandemic_random_coeff_nested_logit.pickle",
                               data_in_unadjust = "02.Intermediate/prepandemic.rds",
                               model_in_adjust = "03.Output/Auxilary_Scale_prepandemic_model.pickle",
                               data_in_adjust = "02.Intermediate/Auxilary_Scale_prepandemic.rds",
                               data_out = "02.Intermediate/prepandemic_Product_Data_Compare.rds");

# Graph MC Differences
spirit_mc_adjust_graph()
spirit_mc_adjust_graph(dollar_graph_out = "05.Figures/Fee_Fix_MC_Graph_Dollar_JBMarket.pdf",
                       percent_graph_out = "05.Figures/Fee_Fix_MC_Graph_Percent_JBMarket.pdf",
                       JB_restrict = TRUE)
spirit_mc_adjust_graph(data_source = "02.Intermediate/prepandemic_Product_Data_Compare.rds",
                                   dollar_graph_out = "05.Figures/Fee_Fix_prepandemic_MC_Graph_Dollar.pdf",
                                   percent_graph_out = "05.Figures/Fee_Fix_prepandemic_MC_Graph_Percent.pdf",
                                   JB_restrict = FALSE,
                       dollar_xlim = c(0, 215))
spirit_mc_adjust_graph(data_source = "02.Intermediate/prepandemic_Product_Data_Compare.rds",
                                   dollar_graph_out = "05.Figures/Fee_Fix_prepandemic_MC_Graph_Dollar_JBMarket.pdf",
                                   percent_graph_out = "05.Figures/Fee_Fix_prepandemic_MC_Graph_Percent_JBMarket.pdf",
                                   JB_restrict = TRUE,
                       dollar_xlim = c(0, 215))


```


# Spirit Exit Simulation
```{r}
spirit_exit_simulation()
```


# Generate Summary Statistics Tables
```{r}
regions_of_note()
hhi_airport_summary()
hhi_airport_summary(input = "02.Intermediate/HHI_Airport_LCC_Market.Rds",
                    output = "06.Tables/HHI_LCC_SummaryStats.tex",
                    mode = "LCC")
major_city_table()
```

# North East Alliance Related Analysis
```{r}
nea_market_mile_price()
avg_mile_price_evolve_graph()
nea_did_construct_data(); gc()
market_yield_reg();
market_fare_reg();
nea_zou_1()
nea_op_carrier_switch(); gc()
nea_op_carrier_graph();
nea_changes_recorded_estimate()
nea_product_details_make();
nea_price_neutrality_yield()
nea_revenue()
nea_product_requirements_table()

# West Coast International Alliance Tables
# share_wcia_table()
```

# Robustness Check: 5%, 10% Effiencies
```{r}
merger_results_table(mode = 5,
                     table_out = "06.Tables/Merger_Results_95.tex")
merger_results_table(mode = 10,
                     table_out = "06.Tables/Merger_Results_90.tex")
minimum_fare_increase_table(mode = 5,
                            table_out = "06.Tables/MinimumFareChange_95.tex")
minimum_fare_increase_table(mode = 10,
                            table_out = "06.Tables/MinimumFareChange_90.tex")

```

# Robustness Check: Logit Estimation
```{r}
# Post-Pandemic
blp_logit_iv(model = linear_component_logit, 
             additional_instruments = instruments, nested = TRUE)
blp_logit_iv(input_file = "02.Intermediate/prepandemic.rds",
            output_file = "03.Output/pre_pandemic_logit_iv.pickle",
             model = linear_component_logit, 
             additional_instruments = instruments, nested = TRUE)

logit_two_period_table()

merger_simulation_advanced(model_in = "03.Output/logit_iv.pickle",
                                       data_in = "02.Intermediate/Product_Data.rds",
                                       data_out = "03.Output/NestedLogit_Adv_Merger_Sim_Data.rds",
                                       mode = "nl")
merger_simulation_advanced(model_in = "03.Output/pre_pandemic_logit_iv.pickle",
                data_in = "02.Intermediate/prepandemic.rds",
                data_out = "03.Output/Prepandemic_NestedLogit_Adv_Merger_Sim_Data.rds",
                                       mode = "nl")

merger_results_table(merger_post = "03.Output/NestedLogit_Adv_Merger_Sim_Data.rds",
                                 observed_post = "02.Intermediate/Product_Data.rds",
                                 merger_pre = "03.Output/Prepandemic_NestedLogit_Adv_Merger_Sim_Data.rds",
                                 observed_pre = "02.Intermediate/prepandemic.rds",
            table_out = "06.Tables/NestedLogit_Merger_Results.tex",
                                 mode = 0)

minimum_fare_increase_table(merger_data.post = "03.Output/NestedLogit_Adv_Merger_Sim_Data.rds",
                                        observed.post = "02.Intermediate/Product_Data.rds",
                                        merger_data.pre =  "03.Output/Prepandemic_NestedLogit_Adv_Merger_Sim_Data.rds",
                                        observed.pre = "02.Intermediate/prepandemic.rds",
                                        table_out = "06.Tables/NestedLogit_MinimumFareChange.tex",
                                        mode = 0)
```


# Robustness Check: City-Pair Markets
```{r}
condense_db1b(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
              output = "02.Intermediate/City_Market_Definition/DB1B_Condensed.rds",
              market_group = c("Year", "Quarter", "Origin.City", "Destination.City"),
              product_group = c("Year", "Quarter", "Origin.City", "Destination.City",
                                "Carrier", "NonStop"))
add_control_variables(input = "02.Intermediate/City_Market_Definition/DB1B_Condensed.rds",
                      output = "02.Intermediate/City_Market_Definition/DB1B_With_Controls.Rds"); gc()
merger_sim_data_generate(years_allowed = 2021:2023,
                         output_file = "02.Intermediate/City_Market_Definition/Post_Pandemic_Product_Data.rds",
                         market_group = c("Year", "Quarter", "Origin.City", "Destination.City"),
              product_group = c("Year", "Quarter", "Origin.City", "Destination.City",
                                "Carrier", "NonStop"))
merger_sim_data_generate(years_allowed = 2017:2019,
                         output_file = "02.Intermediate/City_Market_Definition/Pre_Pandemic_Product_Data.rds",
                         market_group = c("Year", "Quarter", "Origin.City", "Destination.City"),
              product_group = c("Year", "Quarter", "Origin.City", "Destination.City",
                                "Carrier", "NonStop"))
# View Instrument Fit
instrument_comparison_table(input_file = "02.Intermediate/City_Market_Definition/Post_Pandemic_Product_Data.rds",
                            output_file = "06.Tables/CityDefinition_postpandemic_InstrumentTable.tex")
instrument_comparison_table(input_file = "02.Intermediate/City_Market_Definition/Pre_Pandemic_Product_Data.rds",
                            output_file = "06.Tables/CityDefinition_prepandemic_InstrumentTable.tex")



# Demand Estimation
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        input_file = "02.Intermediate/City_Market_Definition/Post_Pandemic_Product_Data.rds",
        output_file = "02.Intermediate/City_Market_Definition/random_coeff_nested_logit_results.pickle",
        precision = 1e-15)

blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        input_file = "02.Intermediate/City_Market_Definition/Pre_Pandemic_Product_Data.rds",
        output_file = "02.Intermediate/City_Market_Definition/PrePandemic_random_coeff_nested_logit_results.pickle",
        precision = 1e-15)

rcl_two_period_table(
   post_in = "02.Intermediate/City_Market_Definition/random_coeff_nested_logit_results.pickle",
   post_data_in = "02.Intermediate/City_Market_Definition/Post_Pandemic_Product_Data.rds",
   pre_in = "02.Intermediate/City_Market_Definition/PrePandemic_random_coeff_nested_logit_results.pickle",
   pre_data_in = "02.Intermediate/City_Market_Definition/Pre_Pandemic_Product_Data.rds",
   output_table = "06.Tables/City_Market_Definition_RCL_Both_Period_Output.tex")


```

# Robustness Check - One Layover or Fewer
```{r}
condense_db1b(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
              output = "02.Intermediate/Construct_DB1B/Layover_Robustness_DB1B_Condensed.rds",
              High_Legs_Cutoff = 3); gc(); gc()
add_control_variables(input = "02.Intermediate/Construct_DB1B/Layover_Robustness_DB1B_Condensed.rds",
                      output = "02.Intermediate/Layover_Robustness_DB1B_With_Controls.Rds"); gc(); gc()
merger_sim_data_generate(years_allowed = 2021:2023,
                         input_file = "02.Intermediate/Layover_Robustness_DB1B_With_Controls.Rds",
                         output_file = "02.Intermediate/Layover_Robustness_Product_Data.rds")
merger_sim_data_generate(years_allowed = 2017:2019,
                          input_file = "02.Intermediate/Layover_Robustness_DB1B_With_Controls.Rds",
                         output_file = "02.Intermediate/Layover_Robustness_Prepandemic_Product_Data.rds")

# Instrument Comparison Tables
instrument_comparison_table(input_file = "02.Intermediate/Layover_Robustness_Product_Data.rds",
                            output_file = "06.Tables/Layover_Robustness_postpandemic_InstrumentTable.tex")
instrument_comparison_table(input_file = "02.Intermediate/Layover_Robustness_Prepandemic_Product_Data.rds",
                            output_file = "06.Tables/Layover_Robustness_prepandemic_InstrumentTable.tex")

# Fit Demand Model
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        input_file = "02.Intermediate/Layover_Robustness_Product_Data.rds",
        output_file = "03.Output/Layover_Robustness_random_coeff_nested_logit_results.pickle",
        precision = 1e-15); 
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        input_file = "02.Intermediate/Layover_Robustness_Prepandemic_Product_Data.rds",
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, 
        nested = TRUE, precision = 1e-15,
        output_file = "03.Output/Layover_Robustness_prepandemic_random_coeff_nested_logit.pickle")

# Report Results
rcl_two_period_table(post_in = "03.Output/Layover_Robustness_random_coeff_nested_logit_results.pickle",
                                 post_data_in = "02.Intermediate/Layover_Robustness_Product_Data.rds",
                                 pre_in = "03.Output/Layover_Robustness_prepandemic_random_coeff_nested_logit.pickle",
                                 pre_data_in = "02.Intermediate/Layover_Robustness_Prepandemic_Product_Data.rds",
                                 output_table = "06.Tables/Layover_Robustness_RCL_Both_Period_Output.tex")

```

# Robustness Check: Add Spirit Average Ancillary Revenue to Each Spirit Ticket
```{r}
condense_db1b(input = "02.Intermediate/Construct_DB1B/DB1B_Clarified.Rds",
              output = "02.Intermediate/Construct_DB1B/Auxilary_Adjust_DB1B_Condensed.rds",
              auxilary_mode = "report")
add_control_variables(input = "02.Intermediate/Construct_DB1B/Auxilary_Adjust_DB1B_Condensed.rds",
                      output = "02.Intermediate/Auxilary_Adjust_DB1B.Rds"); gc()

# # Merger Sim Generate # #
merger_sim_data_generate(years_allowed = 2021:2023,
                         input_file = "02.Intermediate/Auxilary_Adjust_DB1B.Rds",
                         output_file = "02.Intermediate/Auxilary_Adjust_postpandemic.rds")


# Pre-Pandemic
merger_sim_data_generate(years_allowed = 2017:2019,
                         input_file = "02.Intermediate/Auxilary_Adjust_DB1B.Rds",
                         output_file = "02.Intermediate/Auxilary_Adjust_prepandemic.rds")

# Instrument Tables
instrument_comparison_table(input_file = "02.Intermediate/Auxilary_Adjust_postpandemic.rds",
      output_file = "06.Tables/Auxilary_Adjust_Instrument_Compare_Table.tex")
instrument_comparison_table(input_file = "02.Intermediate/Auxilary_Adjust_prepandemic.rds",
      output_file = "06.Tables/Auxilary_Adjust_Prepandemic_Instrument_Compare_Table.tex")

# Estimate Models
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        input_file = "02.Intermediate/Auxilary_Adjust_postpandemic.rds",
        output_file = "03.Output/Auxilary_Adjust_postpandemic_model.pickle",
        precision = 1e-15); 
blp_rcl(additional_instruments = c(hub_interactions, exog_interactions,
                                        rho_instrument), 
        linear = linear_component_rcl,
        nonlinear = nonlinear_component, nested = TRUE,
        input_file = "02.Intermediate/Auxilary_Adjust_prepandemic.rds",
        output_file = "03.Output/Auxilary_Adjust_prepandemic_model.pickle",
        precision = 1e-15)

rcl_two_period_table(post_in = "03.Output/Auxilary_Adjust_postpandemic_model.pickle",
                                 post_data_in = "02.Intermediate/Auxilary_Adjust_postpandemic.rds",
                                 pre_in = "03.Output/Auxilary_Adjust_prepandemic_model.pickle",
                                 pre_data_in = "02.Intermediate/Auxilary_Adjust_prepandemic.rds",
                                 output_table = "06.Tables/Auxilary_Adjust_RCL_Both_Period_Output.tex")

# Merger Simulation
merger_simulation_advanced(model_in = "03.Output/Auxilary_Adjust_prepandemic_model.pickle",
                           data_in = "02.Intermediate/Auxilary_Adjust_prepandemic.rds",
                           data_out = "03.Output/Auxilary_Adjust_Prepandemic_Merger.rds"); gc(); gc(); 
merger_simulation_advanced(model_in = "03.Output/Auxilary_Adjust_postpandemic_model.pickle",
                           data_in = "02.Intermediate/Auxilary_Adjust_postpandemic.rds",
                           data_out = "03.Output/Auxilary_Adjust_Postpandemic_Merger.rds"); gc(); gc()

merger_results_table(merger_post  = "03.Output/Auxilary_Adjust_Postpandemic_Merger.rds",
                     observed_post = "02.Intermediate/Auxilary_Adjust_postpandemic.rds",
                     merger_pre =  "03.Output/Auxilary_Adjust_Prepandemic_Merger.rds",
                     observed_pre = "02.Intermediate/Auxilary_Adjust_prepandemic.rds",
                     table_out = "06.Tables/Auxilary_Adjust_Merger_Results.tex")


minimum_fare_increase_table(
  merger_data.post = "03.Output/Auxilary_Adjust_Postpandemic_Merger.rds",
  observed.post = "02.Intermediate/Auxilary_Adjust_postpandemic.rds",
  merger_data.pre =  "03.Output/Auxilary_Adjust_Prepandemic_Merger.rds",
  observed.pre = "02.Intermediate/Auxilary_Adjust_prepandemic.rds",
  table_out = "06.Tables/Auxilary_Adjust_MinimumFareChange.tex")


```


```{r}
frontier_merger_simulation_advanced(); gc(); gc();
frontier_merger_simulation_advanced(model_in = "03.Output/prepandemic_random_coeff_nested_logit.pickle",
                                    data_in = "02.Intermediate/prepandemic.rds",
                                    data_out = "03.Output/Frontier_Prepandemic_Merger_Sim_Data.rds")
frontier_merger_results_table()
frontier_minimum_fare_percent_increase_table()
```

